\documentclass{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{paralist}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage[inline]{enumitem}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\lstset { %
    language=C++,
    backgroundcolor=\color{black!5}, % set backgroundcolor
    basicstyle=\footnotesize,% basic font setting
}
\title{Directed Study II - Summer 2016}
\author{Kian Davoudi EIT, MASC, PhD Candidate}
\abstract 
The propose of this course is to complete the DD I. The ultimate goal is to identify the possible solution to detect an object in the video stream on the iOS device. In the literature, one could find number of object detection algorithms available. However, although there are much sophisticated algorithms, but, individually their performance is being varied based on the application. Thus, the recommended methodology that I propose in this course, is fist to conduct a survey for applicable solution to object detection in video stream. 

Based on the experience from edge detection aoglrotihm on the iOS device. I make a choice to conduct a parallel development, on iOS as well as OSx. 


\section{Detection of Photoplethysmography from iOS camera}
The algorithm should take an UIImage from iOS AVFoundation inputDevice. Using delegate method, to process UIImage. The function shall estimate the  RGBA from each UIIMage. This is the basic Image processing method that we will use to extract the intensity of the RGBA. Based on tihs value, I will design PPG extraction algorithm. 


\section{Background Information}
\subsection{RGBA primary image type}
RGBA stands for red green blue alpha. While it is sometimes described as a color space, it is actually simply a use of the RGB color model, with extra information. The color is RGB, and may belong to any RGB color space, but an integral alpha value as invented by Catmull and Smith between 1971 and 1972 enables alpha compositing. The inventors named alpha after the Greek letter in the classic linear interpolation formula α A + (1 − α) B.

The alpha channel is normally used as an opacity channel. If a pixel has a value of 0 in its alpha channel, it is fully transparent (and, thus, invisible), whereas a value of 100 in the alpha channel gives a fully opaque pixel (traditional digital images). Values between 0 and 100 make it possible for pixels to show through a background like a glass, an effect not possible with simple binary (transparent or opaque) transparency. It allows easy image compositing.



\section{MyOnwObservation}
Here are my observations, and I would appreciate your feedback:

I have been working on PPG for a long time, and i can almost conformably state that there is no much novel left to innovate with this traditional model that we are using. 
I have came to conclusion, that as long as we continue working with tradition tools, such as matlab, offline data processing its relatively hard to contribute anything new to this field. 

Now, I am really dedicated to proceed with my PhD, and I believe, that a radical change in direction is what is required at this point. Because, I believe that we need a realtime feedback device that we could rely on as a ultimate tool and start designing algorithms for that device. 

Based on my study on machine vision algorithms, although there are many good and sophisticated algorithms in literature, but since the application varies, the efficiency of individual algorithm is being affected too. Thus, many suggest to define an algorithm for particular application. 

OpenCv, is one of the good examples that has came to this conclusion, thus, they are collecting their effort in a platform that is accessible and modifiable on various platforms. 

An other good example is the erfornace of the same algorithms that as used in Labview and Matlab, when I was planning to publish my first paper. The same algorithm with heigh pass filter and the same cut off frequency was providing significantly different results in lavbiew rather matlab. 

We have had conversations with Farzad many times about that platform shall we use. This could be discussed further to come to a suction, however, I believe, given the examples that I have seen in App store, such as xxx, and PPG device could be established and next sophisticated algorithms could be used to perfect performance of such device. 

For that reason I would like to recommend focusing on an app for PPG accusation, or potentially SCG or EEG acquisition on the mobile device. 
One we have this device really, then I plan to apply all statistical methodologies on this device. 

There are numbers of the people trying to extract PPG from iOS but, the question, is which one can provide a more reliable application for this PPG. They have realied soley on HRV, which is something, but what I have is the heahmorrage which is so rare to consuldt. This is my novelty. 


\begin{document}
\maketitle
\bibliographystyle{plain}
\bibliography{references}
\end{document}
